% ICML 2026 Position Paper
% Template: https://icml.cc/Conferences/2026/CallForPapers

\documentclass[letterpaper]{article}

% Required ICML packages
\usepackage{icml2026_templates/icml2026}

% Recommended packages
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{subcaption}

% For algorithms
\usepackage{algorithm}
\usepackage{algorithmic}

% Bibliography
\usepackage{natbib}

% Graphics path - can reference Images/ from parent directory
\graphicspath{{../Images/}{figures/}}

% Custom commands
\newcommand{\eg}{\emph{e.g.}}
\newcommand{\ie}{\emph{i.e.}}
\newcommand{\etal}{\emph{et al.}}

% ==============================================================================
\begin{document}

\twocolumn[
\icmltitle{Forecasting AI Benchmark Saturation: \\
A Hierarchical Bayesian Approach}

% Anonymous submission - remove author info for review
\icmlsetsymbol{equal}{*}

\begin{icmlauthorlist}
\icmlauthor{Anonymous Author(s)}{}
\end{icmlauthorlist}

% \icmlaffiliation{inst1}{Institution 1}
% \icmlcorrespondingauthor{Author Name}{email@domain.com}

\icmlkeywords{AI forecasting, benchmark saturation, Bayesian modeling, capability assessment}

\vskip 0.3in
]

% ==============================================================================
\begin{abstract}
We present a hierarchical Bayesian framework for forecasting the saturation timeline of AI benchmarks.
Analyzing 60 benchmarks spanning cognitive and operational capabilities, we find that nearly all current benchmarks---including the most challenging ones---are projected to saturate before 2030.
Our methodology introduces three innovations: (1) Harvey growth curves to capture asymmetric progress trajectories, (2) frontier-focused modeling to approximate maximum achievable performance, and (3) joint hierarchical inference enabling statistical borrowing across benchmarks.
Security-critical benchmarks (cybersecurity, AI R\&D automation, advanced mathematics) show trajectories suggesting saturation by 2028.
We discuss implications for capability assessment and the limitations of current evaluation paradigms.
\end{abstract}

% ==============================================================================
\section{Introduction}
\label{sec:introduction}

% TODO: Write introduction
% Key points:
% - Rapid progress on AI benchmarks
% - Need for forecasting methods
% - Limitations of current approaches
% - Our contributions

\section{Related Work}
\label{sec:related}

% TODO: Literature review
% - Benchmark forecasting (Steinhardt, Epoch AI)
% - Scaling laws (Kaplan et al., Hoffmann et al.)
% - Observational scaling laws (Ruan et al.)
% - Metabench, Rosetta Stone for AI Benchmarks

\section{Methodology}
\label{sec:methodology}

\subsection{Problem Formulation}
\label{subsec:problem}

% TODO: Formal problem statement

\subsection{Harvey Growth Model}
\label{subsec:harvey}

The Harvey model generalizes the logistic curve by introducing an asymmetry parameter $\alpha$:
\begin{equation}
    f(t) = \frac{L}{\left(1 + (\alpha - 1) e^{-k(t - t_0)}\right)^{1/(\alpha-1)}}
\end{equation}
where $L$ is the upper asymptote, $k$ is the growth rate, $t_0$ is the inflection point, and $\alpha > 1$ controls the asymmetry. When $\alpha = 2$, the Harvey curve reduces to the standard logistic.

\subsection{Hierarchical Bayesian Framework}
\label{subsec:hierarchical}

% TODO: Full model specification
% - Likelihood
% - Priors
% - Hyperpriors

\subsection{Frontier-Focused Modeling}
\label{subsec:frontier}

% TODO: Explain skewed observation model
% - Latent capability vs observed performance
% - Elicitation gap

\section{Experimental Setup}
\label{sec:experiments}

\subsection{Benchmark Selection}
\label{subsec:benchmarks}

% TODO: Describe 60 benchmarks
% - Sources: Epoch AI, Scale AI, RAND
% - Categories and tiers

\subsection{Data Processing}
\label{subsec:data}

% TODO: Normalization, lower bounds, frontier extraction

\section{Results}
\label{sec:results}

\subsection{Saturation Projections}
\label{subsec:saturation}

% TODO: Main results
% - 97% benchmarks saturated by 2030
% - Security-critical by 2028

\subsection{Model Validation}
\label{subsec:validation}

% TODO: Calibration, Harvey vs Logistic comparison

\subsection{Asymmetry Analysis}
\label{subsec:asymmetry}

% TODO: Figure S1 equivalent - asymmetry of growth curves

\section{Discussion}
\label{sec:discussion}

% TODO:
% - Implications for AGI timelines
% - Limitations of benchmarks
% - Heterogeneity of progress
% - Need for new evaluation paradigms

\section{Limitations}
\label{sec:limitations}

% TODO:
% - Benchmark selection bias
% - Extrapolation uncertainty
% - Elicitation gap not fully captured

\section{Conclusion}
\label{sec:conclusion}

% TODO: Summary and future directions

% ==============================================================================
% Acknowledgements (for camera-ready only)
% \section*{Acknowledgements}

% ==============================================================================
\bibliography{references}
\bibliographystyle{icml2026_templates/icml2026}

% ==============================================================================
% Appendix
\appendix
\section{Benchmark Details}
\label{app:benchmarks}

\section{Prior Specifications}
\label{app:priors}

\section{Additional Results}
\label{app:results}

\end{document}
